\bf On semidefinite-representable sets over valuation fields

### 2025-03-17 article/paper_padic_spec.tex
commit by Simone

  Thus we have\footnote{\simone{Est-ce vrai parce que $P_E$ est affine? Car en général il faut que
    $f$ soit injective}} $f(P) = f(P_I) \cap f(P_E)$. However $P_E$ is either empty or an affine subspace of
  $K^n$ and therefore $f(P_E)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
  Hence, as the class of polyhedra is closed under intersection, in order to prove that
  $f(P)$ is a polyhedron, it is sufficient to prove that this holds for $f(P_I)$.
\end{remark}

>>>>

  Thus we have\footnote{\simone{Ça n'est pas vrai en général, il faut que $f$ soit injective.
    Il faut peut être d'abord factoriser $f = g \circ h$ avec $h : K^n \to im(f)$ et
    $g : im(f) \subset K^m$.}}
  $f(P) = f(P_I) \cap f(P_E)$. However $P_E$ is either empty or an affine subspace of
  $K^n$ and therefore $f(P_E)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
  Hence, as the class of polyhedra is closed under intersection, in order to prove that
  $f(P)$ is a polyhedron, it is sufficient to prove that this holds for $f(P_I)$.
\end{remark}
